Measuring Individual Partisan Harm in Redistricting

### 2021-09-12 paper/paper.Rmd
nj example plots

@@

# Relationship Between Districting Metrics in New Jersey {#app:nj}

```{r nj-pairs, fig.cap="Scatterplots for all pairs of metrics. Color indicates the number of Democratic seats won (ranging from 7 to 10). Below the diagonal, numbers indicate the absolute value of the correlation between variables.", fig.width=7, fig.height=7}
include_graphics(here("paper/figures/nj_pairs.pdf"))
```

>>>>

```{r nj-district-shares, fig.cap="Distribution of district vote shares, with districts ordrered by baseline Democratic two-part vote share. Displayed on top are the district vote shares for six example plans, each extremal for some combination of districting measures.", fig.width=6.5, fig.height=3.9}
include_graphics(here("paper/figures/nj_district_shares.pdf"))
```

This is manifested in the district-level vote shares shown in Figure \ref{fig:nj-district-shares}.
Within each districting plan, we number districts in order of their Democratic vote share, with district 1 the least Democratic.
The figure shows these vote shares for six selected districting plans, and compares them to the distribution of shares for the entire sample.
The selected plans themselves are shown in Appendix \ref{app:nj}.

@@

# Districting Measures in New Jersey {#app:nj}

```{r nj-pairs, fig.cap="Scatterplots for all pairs of measures. Color indicates the number of Democratic seats won (ranging from 7 to 10). Below the diagonal, numbers indicate the absolute value of the correlation between variables.", fig.width=7, fig.height=7}
include_graphics(here("paper/figures/nj_pairs.pdf"))
```

```{r nj-ex-maps, fig.cap="Example districting plans selected according to their scores on $F(q)$, $U^{(G)}$, and $U^{(L)}$. District shares for these example plans are shown in Figure \\ref{fig:nj-district-shares}.", fig.width=7, fig.height=7}
include_graphics(here("paper/figures/nj_ex_maps.pdf"))
```
